\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png} \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}

### 2024-01-19 text/paper/paper.tex
tenso

\begin{equation}
    \begin{split}
        E[\text{MeV}] &= m_0 \times E[\text{Chn}] + b_0 \\
        m_0 &= 9.20 \pm 0.06 \\
        b_0 &= 30.22 \pm 34.64
    \end{split}
    \label{eq:calib0}
\end{equation}

@@

\begin{equation}
    \begin{split}
        E[\text{MeV}] &= m_1 \times E[\text{Chn}] + b_1 \\
        m_1 &= 8.97 \pm 0.03 \\
        b_1 &= 55.40 \pm 17.53
    \end{split}
    \label{eq:calib1}
\end{equation}

@@

\begin{equation}
    \begin{split}
        E[\text{MeV}] &= m_2 \times E[\text{Chn}] + b_2 \\
        m_2 &= 9.07 \pm 0.12 \\
        b_2 &= 48.17 \pm 69.69
    \end{split}
    \label{eq:calib2}
\end{equation}

\section{ Lithium Fluoride Sample}

$\ce{LiF}$

@@

$\ce{LiAlO_2}$

@@

>>>>

\begin{equation}
    \begin{split}
        E[\text{keV}] &= m_0 \times E[\text{Chn}] + b_0 \\
        m_0 &= 9.20 \pm 0.06 \\
        b_0 &= 30.22 \pm 34.64
    \end{split}
    \label{eq:calib0}
\end{equation}

@@

\begin{equation}
    \begin{split}
        E[\text{keV}] &= m_1 \times E[\text{Chn}] + b_1 \\
        m_1 &= 8.97 \pm 0.03 \\
        b_1 &= 55.40 \pm 17.53
    \end{split}
    \label{eq:calib1}
\end{equation}

@@

\begin{equation}
    \begin{split}
        E[\text{keV}] &= m_2 \times E[\text{Chn}] + b_2 \\
        m_2 &= 9.07 \pm 0.12 \\
        b_2 &= 48.17 \pm 69.69
    \end{split}
    \label{eq:calib2}
\end{equation}

\section{Alpha Peaks}
For the analysis, we began by calculating the theoretical energy values of the two alphas.

\begin{center}
    \label{alfa_peaks}
    \centering
    \includegraphics[scale = 0.35]{images/AlphaPeaks.png}
    \captionof{figure}{Theoretical energy values of the two alfas}
\end{center}

The energies obtained were 7629.80 kEv and 11031.44 kEv. (FALTA EXPLICAR PERCENTAGENS)

\section{Lithium Fluoride Sample}

The obtained spectrum for the lithium fluoride sample overlapped with the theoretical alpha values is the following:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.6]{../images/SampleLiF.png}
    \captionof{figure}{Spectrum of the $\ce{LiF}$ sample}
\end{center}

There are three noticeable structures in this spectrum. 
The first one is a peak around channel 0, followed a less intense one around 100 Chn and a small plateau between 150 and 250 Chn. 
Lastly there is an evident energy profile that starts at around 300 Chn and goes up to 900 Chn with increasing intensity.

\paragraph*{}

After identifying these structures we used the previous calibration [\ref{sec:calibration}] to convert the channel values into energy values so that we could more effectively analyse the spectrum and its peaks.

@@

We obtained the following spectrum for the lithium aluminate sample:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.6]{../images/SampleLiAlO2.png}
    \captionof{figure}{Spectrum of the $\ce{LiAlO_2}$ sample}
\end{center}

@@

The obtained spectrum for the implanted sample was the following:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.6]{../images/ImplantedSample.png}
    \captionof{figure}{Spectrum of the implanted sample}
\end{center}
